Competing Constructions for German Measure Noun Phrases: from Usage Data to Experiment

### 2017-05-10 Latex/article.tex
Minor fixes, references.

\usepackage[firstpage]{draftwatermark}
\SetWatermarkFontSize{40pt}
\SetWatermarkHorCenter{300pt}
\SetWatermarkColor[rgb]{1,0.2,0.2}
\SetWatermarkText{\textsf{Submitted April 2017.}}

@@

The first experiment tests preferences for constructions explicitly.
\cite{FordBresnan2013} use the \textit{split-100} task in which participants have to distribute 100 points between the alternatives, assigning more points to more natural sounding alternative.
In essence, participants distribute a probability mass between two alternants, which is intended to produce more subtle results compared to a two-alternative forced-choice task such as in \cite{Rosenbach2013}, where participants have to choose one of two alternants.
The split-100 paradigm has been criticised in \cite{ArppeJaervikivi2007}.
The criticism was reiterated in \cite{DivjakEa2016}, where they use a forced-choice task.
In \cite{VerhoevenTemme2017}, it was shown that results from forced-choice and split-100 experiments mostly converge, which is expected in the long run if a probability is turned into a binary decision.
I present a forced-choice experiment in this Section and not a split-100 experiment, mainly because in a dry run of the experiment, participants complained about the unnaturalness of distributing a probability mass across two alternants.
Participants had to choose between two sentences that differed only in that one contained the \NACa\ and the other contained the \PGCa.
The analysis compares the probabilities assigned to stimuli by the corpus-derived model with the frequency with which participants chose the alternants for the same stimuli.

There were 24 participants (native speakers of German without reading or writing disabilities) aged 19 to 30 living permanently in [name of city redacted], who were recruited from introductory linguistics courses at [name of university redacted].
Although the experiment was conducted in the last four weeks of their first semester, participants had no deeper explicit knowledge of linguistics, grammar, or experimental methods.
None of them had ever participated in a forced-choice experiment before.
Participation was voluntary but participants received credit in partial fulfillment of course requirements.

>>>>

\usepackage[firstpage]{draftwatermark}
\SetWatermarkFontSize{30pt}
\SetWatermarkHorCenter{300pt}
\SetWatermarkColor[rgb]{0.9,0.5,0.5}
\SetWatermarkText{\textsf{Submitted April 2017. Do not quote.}}

@@

The first experiment tests preferences for constructions explicitly.
\cite{FordBresnan2013} use the \textit{split-100} task in which participants have to distribute 100 points between the alternatives, assigning more points to more natural sounding alternative.
In essence, participants distribute a probability mass between two alternants, which is intended to produce more subtle results compared to a two-alternative forced-choice task such as in \cite{Rosenbach2013}, where participants have to choose one of two alternants.
The split-100 paradigm has been criticised in \cite{ArppeJaervikivi2007}.
The criticism was reiterated in \cite{DivjakEa2016}, where they use a forced-choice task.
In \cite{VerhoevenTemme2017}, it was shown that results from forced-choice and split-100 experiments mostly converge (with some numeric intricacies related to the non-linear distribution of preferences for alternants).
I present a forced-choice experiment in this Section and not a split-100 experiment, mainly because in a dry run of the experiment, participants complained about the unnaturalness of distributing a probability mass across two alternants.
Participants had to choose between two sentences that differed only in that one contained the \NACa\ and the other contained the \PGCa.
The analysis compares the probabilities assigned to stimuli by the corpus-derived model with the frequency with which participants chose the alternants for the same stimuli.

There were 24 participants (native speakers of German without reading or writing disabilities) aged 19 to 30 living permanently in Berlin, who were recruited from introductory linguistics courses at Freie Universität Berlin.
Although the experiment was conducted in the last four weeks of their first semester, participants had no deeper explicit knowledge of linguistics, grammar, or experimental methods.
None of them had ever participated in a forced-choice experiment before.
Participation was voluntary but participants received credit in partial fulfillment of course requirements.
